---
title: "Solar Energy Industry Stocks Statistical Analysis"
author: "YuejieJin&YuqiLiu&Yue Zhao"
date: "2017-12-13"
output: word_document
---

##
* ## Data preparation
```{r}
library(quantmod)
library(ggplot2)
library(mgcv)
```

```{r Data}
## ---------------------------------------------------------------------------------------------------------------
## ----------------------------------------Response Variables-----------------------------------------------------
## Solar Industry ------------------------------------------------------------------------------------------------
# First Solar, Inc. (FSLR) 
FSLR = as.data.frame(getSymbols(Symbols = "FSLR", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
# China Sunergy Co., Ltd. (CSUNY)
CSUNY = as.data.frame(getSymbols(Symbols = "CSUNY", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
# Guggenheim Solar ETF (TAN)
TAN = as.data.frame(getSymbols(Symbols = "TAN", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))

## ---------------------------------------------------------------------------------------------------------------
## ----------------------------------------Explanatory Variables--------------------------------------------------
## Downstream Industry -------------------------------------------------------------------------------------------
#SunPower Corporation (SPWR)
SPWR = as.data.frame(getSymbols(Symbols = "SPWR", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
#SunEdison, Inc. (SUNEQ)
SUNEQ = as.data.frame(getSymbols(Symbols = "SUNEQ", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
#Public Service Enterprise Group Incorporated (PEG)
PEG = as.data.frame(getSymbols(Symbols = "PEG", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))

## Upstream Industry -------------------------------------------------------------------------------------------
#Silicon Laboratories Inc. (SLAB)
SLAB = as.data.frame(getSymbols(Symbols = "SLAB", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))

## Related Industry -------------------------------------------------------------------------------------------
#oil: Chevron Corporation (CVX)
CVX = as.data.frame(getSymbols(Symbols = "CVX", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
#Energy Select Sector SPDR ETF (XLE)
XLE = as.data.frame(getSymbols(Symbols = "XLE", from = "2012-11-09", to = "2016-11-09",auto.assign = FALSE))
```

```{r Calculate Returns}
p_close = data.frame(row.names = rownames(FSLR), First_Solar = FSLR[,6], China_Sunergy = CSUNY[,6], Solar_ETF = TAN[,6], Sun_Power = SPWR[,6], Sun_Edison = SUNEQ[,6], PSE_G = PEG[,6], Silicon=SLAB[,6], Chevron = CVX[,6], Energy_ETF = XLE[,6])

returns <- data.frame(cbind.data.frame(diff(as.matrix(p_close))/(p_close)[-1,]))
summary(returns)
```
##
* ## Correlation Analysis
```{r correlation matrix between the explanatory variables}
plot(returns)

# Explanatory
dfvariable= returns[,c(-1,-2,-3)]
plot(dfvariable, gap=0)

VIF = diag(solve(cor(dfvariable)))  ## Variance Inflation Factors
VIF
round(cor(dfvariable),2)

# Response
returnsesponse= returns[,c(-4,-5,-6,-7,-8,-9)]
plot(returnsesponse, gap=0)

VIF = diag(solve(cor(returnsesponse)))  ## Variance Inflation Factors
VIF
round(cor(returnsesponse),2)
```
It seems that Chevron and Energy_ETF have high variance inflation factors, indicating that they perhaps should be dropped. The correlation matrix suggest that there's a strong relationship between Chevron and Energy_ETF (r = 0.87). This is because Chevron Corporation (CVX) is one of the largest underlying components of Energy Select Sector SPDR ETF (XLE).

It seems that First Solar and Solar ETF have not small variance inflation factors, indicating that they perhaps should be dropped. The correlation matrix suggest that there's a relationship between First Solar and Solar ETF (r = 0.67). This is because the First Solar is one of the underlying components of Solar ETF, but China Sunergy is a company from China.

##
* ## Simple Linear Regression
```{r Simple Linear Regression and Compare R-squared - First Solar}
# Find the best fit
r_square_fs <- c()
for (i in 4:9)
{
  temp <- summary(lm(First_Solar~returns[,i], data=returns))
  r_square_fs <- c(r_square_fs,temp$adj.r.squared)
}
r_square_fs <- as.matrix(r_square_fs)
rownames(r_square_fs) <- c("Sun_Power","Sun_Edison","PSE_G","Silicon","Chevron","Energy_ETF")
r_square_fs

# Linear
fs_model1 <- lm(First_Solar~Sun_Power, data=returns)
summary(fs_model1)
par(mfrow=c(1,2))
plot(fs_model1, which=c(1,2))
# Polynomial
fs_model2 <- lm(First_Solar~poly(Sun_Power, 3), data=returns)
summary(fs_model2)
par(mfrow=c(1,2))
plot(fs_model2, which=c(1,2))
anova(fs_model1,fs_model2, test = "Chisq")
# GAM
fs_model3 <- gam(First_Solar~s(Sun_Power), data=returns)
summary(fs_model3)
plot(fs_model3)
anova(fs_model1,fs_model3, test = "Chisq")

# R-squared
r_square_fs <- matrix(c(summary(fs_model1)$adj.r.squared,summary(fs_model2)$adj.r.squared,summary(fs_model3)$r.sq))
rownames(r_square_fs) <- c("Linear","Poly","GAM")
r_square_fs
```

```{r Simple Linear Regression and Compare R-squared - China Sunergy}
# Find the best fit
r_square_cs <- c()
for (i in 4:9)
{
  temp <- summary(lm(China_Sunergy~returns[,i], data=returns))
  r_square_cs <- c(r_square_cs,temp$adj.r.squared)
}
r_square_cs <- as.matrix(r_square_cs)
rownames(r_square_cs) <- c("Sun_Power","Sun_Edison","PSE_G","Silicon","Chevron","Energy_ETF")
r_square_cs

# Linear
cs_model1 <- lm(China_Sunergy~Sun_Edison, data=returns)
summary(cs_model1)
par(mfrow=c(1,2))
plot(cs_model1, which=c(1,2))
# Polynomial
cs_model2 <- lm(China_Sunergy~poly(Sun_Edison,7), data=returns)
summary(cs_model2)
par(mfrow=c(1,2))
plot(cs_model2, which=c(1,2))
anova(cs_model1,cs_model2, test = "Chisq")
# GAM
cs_model3 <- gam(China_Sunergy~s(Sun_Edison), data=returns)
summary(cs_model3)
plot(cs_model3)
anova(cs_model1,cs_model3, test = "Chisq")

# R-squared
r_square_cs <- matrix(c(summary(cs_model1)$adj.r.squared,summary(cs_model2)$adj.r.squared,summary(cs_model3)$r.sq))
rownames(r_square_cs) <- c("Linear","Poly","GAM")
r_square_cs
```

```{r Simple Linear Regression and Compare R-squared - Guggenheim Solar ETF }
# Find the best fit
r_square_se <- c()
index <- c(1,2,4,5,6,7,8,9)
for (i in index)
{
  temp <- summary(lm(Solar_ETF~returns[,i], data=returns))
  r_square_se <- c(r_square_se,temp$adj.r.squared)
}
r_square_se <- as.matrix(r_square_se)
rownames(r_square_se) <- c("First_Solar","China_Sunergy","Sun_Power","Sun_Edison","PSE_G","Silicon","Chevron","Energy_ETF")
r_square_se

# Linear
se_model1 <- lm(Solar_ETF~Sun_Power, data=returns)
summary(se_model1)
par(mfrow=c(1,2))
plot(se_model1, which=c(1,2))
# Polynomial
se_model2 <- lm(Solar_ETF~poly(Sun_Power,6), data=returns)
summary(se_model2)
par(mfrow=c(1,2))
plot(se_model2, which=c(1,2))
anova(se_model1,se_model2, test = "Chisq")
# GAM
se_model3 <- gam(Solar_ETF~s(Sun_Power), data=returns)
summary(se_model3)
plot(se_model3)
anova(se_model1,se_model3, test = "Chisq")

# R-squared
r_square_se <- matrix(c(summary(se_model1)$adj.r.squared,summary(se_model2)$adj.r.squared,summary(se_model3)$r.sq))
rownames(r_square_se) <- c("Linear","Poly","GAM")
r_square_se
```

##
* ## Multiple regression
```{r Multiple Regression and Compare R-squared - First Solar}
# Stepwise Selection
null.model <- lm(First_Solar ~ 1, data=returns)
full.model <- lm(First_Solar~Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF, data=returns)
full.model.formula <- First_Solar~Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF
stepwise_FS_all  <- step( null.model, full.model.formula, trace=0)
stepwise_FS_all

# Linear
FS_lr_a <- lm(formula = First_Solar ~ Sun_Power + Energy_ETF + Sun_Edison + Silicon, data = returns)
summary(FS_lr_a)
par(mfrow=c(1,2))
plot(FS_lr_a, which=c(1,2))
# Polynomial
FS_ply_a <- lm(formula = First_Solar ~ poly(Sun_Power,4) + poly(Energy_ETF,1) + poly(Sun_Edison,1) + poly(Silicon,1), data = returns)
summary(FS_ply_a)
par(mfrow=c(1,2))
plot(FS_ply_a, which=c(1,2))
anova(FS_lr_a,FS_ply_a, test = "Chisq")
# GAM
FS_gam_a <- gam(formula = First_Solar ~ s(Sun_Power) + s(Energy_ETF) + s(Sun_Edison) + s(Silicon), data = returns)
summary(FS_gam_a)
par(mfrow=c(1,2))
plot(FS_gam_a)
anova(FS_lr_a,FS_gam_a, test = "Chisq")

# R-squared
r_square_fs2 <- matrix(c(summary(FS_lr_a)$adj.r.squared,summary(FS_ply_a)$adj.r.squared,summary(FS_gam_a)$r.sq))
rownames(r_square_fs2) <- c("Linear","Poly","GAM")
r_square_fs2
```

```{r Multiple Regression and Compare R-squared - China Sunergy}
# Stepwise Selection
null.model <- lm(China_Sunergy ~ 1, data=returns)
full.model <- lm(China_Sunergy~Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF, data=returns)
full.model.formula <- China_Sunergy~Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF
stepwise_CS_all  <- step( null.model, full.model.formula, trace=0)
stepwise_CS_all

# Linear
CS_lr_a <- lm(formula = China_Sunergy ~ Sun_Edison + Sun_Power + Silicon, data = returns)
summary(CS_lr_a)
par(mfrow=c(1,2))
plot(CS_lr_a, which=c(1,2))
# Polynomial
CS_ply_a <- lm(formula = China_Sunergy ~ poly(Sun_Edison,8) + poly(Sun_Power,1) + poly(Silicon,5), data = returns)
summary(CS_ply_a)
par(mfrow=c(1,2))
plot(CS_ply_a, which=c(1,2))
anova(CS_lr_a,CS_ply_a, test = "Chisq")
# GAM
CS_gam_a <- gam(formula = China_Sunergy ~ s(Sun_Edison) + s(Sun_Power) + s(Silicon), data = returns)
summary(CS_gam_a)
par(mfrow=c(1,2))
plot(CS_gam_a)
anova(CS_lr_a,CS_gam_a, test = "Chisq")

# R-squared
r_square_cs2 <- matrix(c(summary(CS_lr_a)$adj.r.squared,summary(CS_ply_a)$adj.r.squared,summary(CS_gam_a)$r.sq))
rownames(r_square_cs2) <- c("Linear","Poly","GAM")
r_square_cs2
```

```{r Multiple Regression and Compare R-squared - Guggenheim Solar ETF}
# Stepwise Selection
null.model <- lm(Solar_ETF ~ 1, data=returns)
full.model <- lm(Solar_ETF~First_Solar+China_Sunergy+Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF, data=returns)
full.model.formula <- Solar_ETF~First_Solar+China_Sunergy+Sun_Power+Sun_Edison+PSE_G+Silicon+Chevron+Energy_ETF
stepwise_SE_all  <- step( null.model, full.model.formula, trace=0)
stepwise_SE_all

# Linear
SE_lr_a <- lm(formula = Solar_ETF ~ Sun_Power + First_Solar + Energy_ETF + Sun_Edison + Silicon + China_Sunergy, data = returns)
summary(SE_lr_a)
par(mfrow=c(1,2))
plot(SE_lr_a, which=c(1,2))
# Polynomial
SE_ply_a <- lm(formula = Solar_ETF ~ poly(Sun_Power,7) + poly(First_Solar,11) + poly(Energy_ETF,4) + poly(Sun_Edison,4) + poly(Silicon,3) + poly(China_Sunergy,4), data = returns)
summary(SE_ply_a)
par(mfrow=c(1,2))
plot(SE_ply_a, which=c(1,2))
anova(SE_lr_a,SE_ply_a, test = "Chisq")
# GAM
SE_gam_a <- gam(formula = Solar_ETF ~ s(Sun_Power) + s(First_Solar) + s(Energy_ETF) + s(Sun_Edison) + s(Silicon) + s(China_Sunergy), data = returns)
summary(SE_gam_a)
par(mfrow=c(1,2))
plot(SE_gam_a)
anova(SE_lr_a,SE_gam_a, test = "Chisq")

# R-squared
r_square_SE2 <- matrix(c(summary(SE_lr_a)$adj.r.squared,summary(SE_ply_a)$adj.r.squared,summary(SE_gam_a)$r.sq))
rownames(r_square_SE2) <- c("Linear","Poly","GAM")
r_square_SE2
```

##
* ## Logistic regression
```{r logistic regression}
attach(returns)
FSLR_level = c()
for (i in 1:length(First_Solar)){
  if (First_Solar[i] > 0) {
    FSLR_level = c(FSLR_level, 1)}
  else{FSLR_level = c(FSLR_level, 0)}}
FSLR_level = factor(FSLR_level)
L_model1 <- glm(FSLR_level ~ Sun_Power + Sun_Edison + PSE_G + Silicon + Chevron + Energy_ETF, family = binomial(link = "logit"))
L_model1 <- step(L_model1, direction = "backward",trace = 0)

CSUNY_level = c()
for (i in 1:length(China_Sunergy)){
  if (China_Sunergy[i] >= 0) {
    CSUNY_level = c(CSUNY_level, 1)}
  else{CSUNY_level = c(CSUNY_level, 0)}}
CSUNY_level = factor(CSUNY_level)
L_model2 <- glm(CSUNY_level ~ Sun_Power + Sun_Edison + PSE_G + Silicon + Chevron + Energy_ETF, family = binomial(link = "logit"))
L_model2 <- step(L_model2, direction = "backward",trace = 0)


TAN_level = c()
for (i in 1:length(Solar_ETF)){
  if (Solar_ETF[i] > 0) {
    TAN_level = c(TAN_level, 1)}
  else{TAN_level = c(TAN_level, 0)}}
TAN_level = factor(TAN_level)
L_model3 <- glm(TAN_level ~ First_Solar+ Sun_Power + Sun_Edison + PSE_G + Silicon + Chevron + Energy_ETF, family = binomial(link = "logit"))
L_model3 <- step(L_model3, direction = "backward",trace = 0)

detach(returns)
```

##
* ## Test the models
```{r Data}
## ---------------------------------------------------------------------------------------------------------------
## ----------------------------------------Response Variables-----------------------------------------------------
## Solar Industry ------------------------------------------------------------------------------------------------
# First Solar, Inc. (FSLR) 
FSLR2 = as.data.frame(getSymbols(Symbols = "FSLR", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
# China Sunergy Co., Ltd. (CSUNY)
CSUNY2 = as.data.frame(getSymbols(Symbols = "CSUNY", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
# Guggenheim Solar ETF (TAN)
TAN2 = as.data.frame(getSymbols(Symbols = "TAN", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))

## ---------------------------------------------------------------------------------------------------------------
## ----------------------------------------Explanatory Variables--------------------------------------------------
## Downstream Industry -------------------------------------------------------------------------------------------
#SunPower Corporation (SPWR)
SPWR2 = as.data.frame(getSymbols(Symbols = "SPWR", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
#SunEdison, Inc. (SUNEQ)
SUNEQ2 = as.data.frame(getSymbols(Symbols = "SUNEQ", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
#Public Service Enterprise Group Incorporated (PEG)
PEG2 = as.data.frame(getSymbols(Symbols = "PEG", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))

## Upstream Industry -------------------------------------------------------------------------------------------
#Silicon Laboratories Inc. (SLAB)
SLAB2 = as.data.frame(getSymbols(Symbols = "SLAB", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))

## Related Industry -------------------------------------------------------------------------------------------
#oil: Chevron Corporation (CVX)
CVX2 = as.data.frame(getSymbols(Symbols = "CVX", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
#Energy Select Sector SPDR ETF (XLE)
XLE2 = as.data.frame(getSymbols(Symbols = "XLE", from = "2016-11-09", to = "2017-11-09",auto.assign = FALSE))
```

```{r Calculate Returns}
p_close2 = data.frame(row.names = rownames(FSLR2), First_Solar = FSLR2[,6], China_Sunergy = CSUNY2[,6], Solar_ETF = TAN2[,6], Sun_Power = SPWR2[,6], Sun_Edison = SUNEQ2[,6], PSE_G = PEG2[,6], Silicon=SLAB2[,6], Chevron = CVX2[,6], Energy_ETF = XLE2[,6])

returns2 <- data.frame(cbind.data.frame(diff(as.matrix(p_close2))/(p_close2)[-1,]))
summary(returns2)
```

```{r testing models - SSE}
sum((predict(fs_model3, returns2) - returns2$First_Solar)^2)/length(returns2$First_Solar)
sum((predict(cs_model3, returns2) - returns2$China_Sunergy)^2)/length(returns2$China_Sunergy)
sum((predict(se_model2, returns2) - returns2$Solar_ETF)^2)/length(returns2$Solar_ETF)
sum((predict(FS_gam_a, returns2) - returns2$First_Solar)^2)/length(returns2$First_Solar)
sum((predict(CS_gam_a, returns2) - returns2$China_Sunergy)^2)/length(returns2$China_Sunergy)
sum((predict(SE_gam_a, returns2) - returns2$Solar_ETF)^2)/length(returns2$Solar_ETF)
```

```{r testing models - accuracy}
attach(returns2)
FSLR_level_t = c()
for (i in 1:length(First_Solar)){
  if (First_Solar[i] > 0) {
    FSLR_level_t = c(FSLR_level_t, 1)}
  else{FSLR_level_t = c(FSLR_level_t, 0)}}
FSLR_level_t = factor(FSLR_level_t)

CSUNY_level_t = c()
for (i in 1:length(China_Sunergy)){
  if (China_Sunergy[i] > 0) {
    CSUNY_level_t = c(CSUNY_level_t, 1)}
  else{CSUNY_level_t = c(CSUNY_level_t, 0)}}
CSUNY_level_t = factor(CSUNY_level_t)

TAN_level_t = c()
for (i in 1:length(Solar_ETF)){
  if (Solar_ETF[i] > 0) {
    TAN_level_t = c(TAN_level_t, 1)}
  else{TAN_level_t = c(TAN_level_t, 0)}}
TAN_level_t = factor(TAN_level_t)

sum(round(predict(L_model1,newdata = returns2,type = "response"))==FSLR_level_t)/length(First_Solar)
sum(round(predict(L_model2,newdata = returns2,type = "response"))==CSUNY_level_t)/length(China_Sunergy)
sum(round(predict(L_model3,newdata = returns2,type = "response"))==TAN_level_t)/length(Solar_ETF)

detach(returns2)
```
